Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-13 paper/related_work.tex
Related work review.

NeuroProof \cite{neuroproof2013} tries to decrease error rates with interactive learning of agglomeration of over-segmentations of images, based on a random forest classifier. Vazquez-Reina \etal~\cite{amelio_segmentation} propose automatic 3D segmentation by taking whole EM volumes into account rather than a per section approach, then solving a fusion problem with a global context. Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion. It is also possible to learn segmentation classification features directly from images with CNNs. Ronneberger \etal~\cite{RonnebergerFB15} use a contracting/expanding CNN path architecture to enable precise boundary localization with small amounts of training data. Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.

Bogovic \etal~\cite{BogovicHJ13} learn 3D features, and show even that unsupervised learning can produce better features than hand-designs. Our work was inspired by this paper and we extend the features reported by Bogovic \etal for our guided proofreading classifiers as described in section \ref{sec:methods}.
These approaches make good progress; however, in general, proofreading is required to correct errors.

\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One way to perform such corrections is by using expert tools such as Raveler introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. This software offers many parameters for tweaking the proofreading process. Created in 2010, Raveler is still used today by professional full-time proofreaders. Many similar systems exist as stand-alone products or plugins to existing visualization system,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.

In contrast to these expert tools, recent works attack the problem of proofreading massive datasets by novices through crowd-sourcing~\cite{saalfeld09,anderson2011,Giuly2013DP2}. A very popular platform is EyeWire presented by Kim \etal~\cite{eyewire_nature}. EyeWire is set up as an online game and participants earn virtual rewards for merging oversegmented labeling to reconstruct the retina cells.
A range of proofreading tools exist in-between expert systems and online games such as Mojo and \textit{Dojo} developed by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}. Mojo provides a simple scribble interface for error correction, and Dojo extends this for distributed proofreading via a minimalistic web-based user interface. The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec. 3 and 4)~\cite{haehn_dojo_2014}. In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.
All interactive proofreading solutions require the user to find potential errors manually which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent works propose computer-aided proofreading systems which help with this visual search task.

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} To reduce the time spent looking for errors, Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}. His approach finds split errors by analyzing segment size ratios across slices and then offers yes/no questions to correct these errors. Plaza reports that additional processing beyond FP is required to find merge errors. His method is freely available as open source software and is integrated into Raveler. This makes it feasible for us to use FP as a baseline for evaluating guided proofreading as described in section \ref{sec:evaluation}.

A similar approach was published by Karimov \etal as guided volume editing~\cite{karimov_guided_volume_editing}. Measuring differences in histogram distributions in image data enables to find potential split and merge errors in the corresponding segmentation. For merge errors, the authors generate possible boundaries using watershed which inspired our approach as described in section \ref{sec:methods}. Guided volume editing was designed to let expert users correct labeled computer-tomography datasets by performing several interactions per correction.

While focused proofreading and guided volume editing both use a heuristical approach to analyze the image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This method is really a segmentation technique but it is possible to use the uncertainty information to present potential regions for proofreading. Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets. Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.

>>>>

Many works tackle this problem. NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier. Vazquez-Reina \etal~\cite{amelio_segmentation} take whole EM volumes into account rather than a per section approach, then solve a fusion problem with a global context. Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion. Bogovic \etal~\cite{BogovicHJ13} learn 3D features unsupervised, and show that they can be better than by-hand designs.

It is also possible to learn segmentation classification features directly from images with CNNs. Ronneberger \etal~\cite{RonnebergerFB15} use a contracting/expanding CNN path architecture to enable precise boundary localization with small amounts of training data. Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.

All these approaches make good progress; however, in general, proofreading is still required to correct errors.

%Inspired by Bogovic \etal, we extend their features for our guided proofreading classifiers (Section \ref{sec:methods}).

\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process. Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.

Recent papers have attacked the problem of proofreading massive datasets through crowdsourcing with novices~\cite{saalfeld09,anderson2011,Giuly2013DP2}. One popular platform is EyeWire, by Kim \etal~\cite{eyewire_nature}, where participants earn virtual rewards for merging oversegmented labeling to reconstruct retina cells.

Between expert systems and online games sit Mojo and \textit{Dojo}, by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces for error correction. Dojo extends this to distributed proofreading via a minimalistic web-based user interface. The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec. 3 and 4)~\cite{haehn_dojo_2014}. In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.

All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}, which finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors. Plaza reports that additional processing beyond FP is required to find merge errors. This method is open source and is integrated into Raveler. We use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).

A similar approach by Karimov \etal, known as guided volume editing~\cite{karimov_guided_volume_editing}, measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This was designed to let expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).

While focused proofreading and guided volume editing both use heuristics to analyze image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user. Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets. Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.
